Residence time, a master variable of ecology, physiology, and natural selection

### 2015-08-07 analyses/2015_06_27_ResTime.Rmd
modifying .Rmd code to produce beautified ggplots for ESA talk -KL

#par(mfrow=c(2, 2))
p1 <- ggplot(data=NULL, aes(x=h.tau, y=t.tau)) +
  geom_point(color="cyan") +
  labs(x= expression(tau), y="Residence Time") +
  labs(title="Tracers") +
  scale_x_log10(limits = c(10, 10000)) + scale_y_log10(limits = c(10, 2000)) +
  coord_fixed(ratio = 1.4) +
  theme_black()

p2 <- ggplot(data=NULL, aes(x=h.tau, y=m.tau)) +
  geom_point(color="magenta") +
  labs(x= expression(tau), y=" ") +
  labs(title="Individuals") +
  scale_x_log10(limits = c(10, 10000)) + scale_y_log10(limits = c(10, 2000)) +
  coord_fixed(ratio = 1.4) +
  theme_black()

p3 <- ggplot(data=NULL, aes(x=h.tau, y=r.tau)) +
  geom_point(color="chartreuse") +
  labs(x= expression(tau), y=" ") +
  labs(title="Resources") +
  scale_x_log10(limits = c(10, 10000)) + scale_y_log10(limits = c(10, 200)) +
  coord_fixed(ratio = 2.38) +
  theme_black()

multiplot(p1, p2, p3, cols=3)

@@

png(filename = '~/GitHub/hydrobide/results/figs/NandS_vs_ResTime.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "white")

par(mfrow=c(1, 2))
num.sims <- max(sim.data$sim)
colors <- rainbow(num.sims)

i <- 0
while (i < num.sims){

  sim.sub <- subset(sim.data, sim == i)
  i <- i + 1
  print(i)

  height <- sim.sub$Height
  width <- sim.sub$Width
  flow.rate <- sim.sub$FlowRate
  e.var <- sim.sub$e.var
  e.simp <- sim.sub$simpson.e
  avg.ab <- N/S
  Skew <-sim.sub$skew
  Nmax <- sim.sub$N.max
  SimpD <- sim.sub$SD

  h.tau <- (height * width)/flow.rate

  N <- sim.sub$N
  S <- sim.sub$S

  x <- c()
  y <- c()
  ct <- 1
  for (val in N){
    if(is.nan(val) == FALSE && val > 0.1){
      y <- c(y, val)
      x <- c(x, h.tau[ct])
      }
    ct <- ct+1
    }

  if (i == 1){
    plot(x, y, xlab="Ecosystem residence time", log="xy",
    ylab="Total Abundance", xlim = c(20, 6000), ylim = c(10, 20000),
    main = "N vs. Tau", col=colors[i])
    lines(x, y, col=colors[i])
    }
  else{
    points(x, y, col=colors[i])
    lines(x, y, col=colors[i])
    }

  }

i <- 0
while (i < num.sims){

  sim.sub <- subset(sim.data, sim == i)
  i <- i + 1

  height <- sim.sub$Height
  width <- sim.sub$Width
  flow.rate <- sim.sub$FlowRate
  e.var <- sim.sub$e.var
  e.simp <- sim.sub$simpson.e
  avg.ab <- N/S
  Skew <-sim.sub$skew
  Nmax <- sim.sub$N.max
  SimpD <- sim.sub$SD

  h.tau <- (height * width)/flow.rate
  S <- sim.sub$S

  x <- c()
  y <- c()
  ct <- 1
  for (val in S){
    if(is.nan(val) == FALSE && val > 0.1){
      y <- c(y, val)
      x <- c(x, h.tau[ct])
      }
    ct <- ct+1
    }

  if (i == 1){
    plot(x, y, xlab="Ecosystem residence time", log="xy",
    ylab="Species richness", xlim = c(20, 6000), ylim = c(2, 50),
    main = "S vs. Tau", col=colors[i])
    lines(x, y, col=colors[i])
    }
  else{
    points(x, y, col=colors[i])
    lines(x, y, col=colors[i])
    }
}

dev.off()

```

@@

png(filename = '~/GitHub/hydrobide/results/figs/Growth_and_Maint.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "white")

par(mfrow=c(1, 2))

growth <- sim.data$avg.per.capita.growth
x <- c()
y <- c()

ct <- 1
for (val in growth){
  if(is.nan(val) == FALSE && val > 0.1){
    y <- c(y, val)
    x <- c(x, h.tau[ct])
    }
  ct <- ct+1
  }

plot(x, y, xlab="Ecosystem residence time", log="x",
     ylab="growth rate", 
     main = "Per capita growth vs. Tau",
     col='dodgerblue')

maint <- (S*sim.data$avg.per.capita.maint)/N
plot(h.tau, maint, xlab="Ecosystem residence time", log="xy",
     ylab="Maintenance", 
     main = "Per capita maintenance vs. Tau",
     col='darkolivegreen')

>>>>

p1 <- ggplot(data=NULL, aes(x=h.tau, y=t.tau)) +
  geom_abline(intercept = 0, slope=1, colour="white", lty=2) +
  geom_point(color="cyan") +
  labs(x= expression(tau), y="Residence Time") +
  labs(title="Tracers") +
  scale_x_log10(limits = c(10, 10000)) + scale_y_log10(limits = c(10, 2000)) +
  coord_fixed(ratio = 1.4) +
  theme_black()

p2 <- ggplot(data=NULL, aes(x=h.tau, y=m.tau)) +
  geom_abline(intercept = 0, slope=1, colour="white", lty=2) +
  geom_point(color="magenta") +
  labs(x= expression(tau), y=" ") +
  labs(title="Individuals") +
  scale_x_log10(limits = c(10, 10000)) + scale_y_log10(limits = c(10, 2000)) +
  coord_fixed(ratio = 1.4) +
  theme_black()

p3 <- ggplot(data=NULL, aes(x=h.tau, y=r.tau)) +
  geom_abline(intercept = 0, slope=1, colour="white", lty=2) +
  geom_point(color="chartreuse") +
  labs(x= expression(tau), y=" ") +
  labs(title="Resources") +
  scale_x_log10(limits = c(10, 10000)) + scale_y_log10(limits = c(10, 200)) +
  coord_fixed(ratio = 2.38) +
  theme_black()

multiplot(p1, p2, p3, cols=3)
dev.off()
```

@@

png(filename = '~/GitHub/hydrobide/results/figs/NandS_vs_ResTime.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

num.sims <- max(sim.data$sim)
colors <- rainbow(num.sims)

p1 <- ggplot(sim.data, aes(x=particle.tau, y=N, group=sim, colour=sim)) +
  scale_color_gradient(high="cyan") +
  geom_line() +
  theme_black() +
  labs(x= expression(tau), y="Individuals") +
  labs(title="Total abundance") +
  guides(colour=FALSE) + 
  scale_x_log10(limits = c(10, 1000)) + 
  scale_y_log10(limits = c(100, 10000)) +
  coord_fixed(ratio = 1)

p2 <- ggplot(sim.data, aes(x=particle.tau, y=S, group=sim, colour=sim)) +
  scale_color_gradient(high="chartreuse") +
  geom_line() +
  theme_black() +
  labs(x= expression(tau), y="Species") +
  labs(title="Numbers of species") +
  guides(colour=FALSE) +
  scale_x_log10(limits = c(10, 1000)) +
  coord_fixed(ratio = .0345)

multiplot(p1, p2, cols=2)
dev.off()
```

@@

png(filename = '~/GitHub/hydrobide/results/figs/Growth_and_Maint.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

growth <- sim.data$avg.per.capita.growth
xs <- c()
ys <- c()

ct <- 1
for (val in growth){
  if(is.nan(val) == FALSE && val > 0.1){
    ys <- c(ys, val)
    xs <- c(xs, h.tau[ct])
    }
  ct <- ct+1
  }

p1 <- ggplot(data=NULL, aes(x=xs, y=ys)) +
  geom_point(colour="magenta") +
  labs(x= expression(tau), y="Growth") +
  labs(title="Growth rate") +
  scale_x_log10(limits = c(20, 1000)) +
  coord_fixed(ratio = 4) +
  theme_black()

maint <- (S*sim.data$avg.per.capita.maint)/N

p2 <- ggplot(data=NULL, aes(x=h.tau, y=maint)) +
  geom_point(colour="cyan") +
  labs(x= expression(tau), y="Maintenance") +
  labs(title="Maintenance") +
  scale_x_log10(limits = c(20, 1000)) +
  scale_y_log10() +
  coord_fixed(ratio = .5) +
  theme_black()

multiplot(p1, p2, cols=2)
dev.off()
```
